Paper Two

### 2023-02-22 Paper Two .qmd
Initial commit

The paper investigates the impact of subway systems on air pollution in cities around the world. It uses two main data sources: a description of the world's subway systems and a measure of airborne particulates, Aerosol Optical Depth (AOD), recorded by satellites between February 2000 and December 2017. The analysis uses a comparison of changes in AOD within a city before and after the opening of a subway system to establish its causal effect. Most of the data and basic analysis are from Nicolas Gendron-Carrier's paper of "Subways and Urban Air Pollution". (@ Subways and Urban Air Pollution)

@@

# Data
All the data that is used for replication in this paper is collected by Nicolas Gendron-Carrier et al. Their study collected data from multiple sources and employed various techniques to analyze the data and draw conclusions about the impact of subway systems on air pollution.

## Pollution Measured by Satellite
The study used satellite imagery to measure the concentration of particulates in the air. The study uses data from satellites to measure the aerosol optical depth (AOD) of the atmosphere at a 3km spatial resolution. The Moderate Resolution Imaging Spectroradiometers on Terra and Aqua earth-observing satellites provide daily AOD measures. The satellite data was collected from the NASA MODIS instrument, which provides measurements of particulate matter at a resolution of 10 kilometers. The satellite data was then combined with ground-based measurements of particulate matter to create a comprehensive dataset that could be used to analyze the impact of subway systems on air pollution. (@Remer, L. A., S. Mattooand R. C. Levy, and L. A. Munchak. 2013. Modis 3km aerosol product: algorithm and global perspective. Atmospheric Measurement Techniques 6: 1829–1844.)

## Subway Data
Furthermore, the study also collected data on the opening of subway systems in various cities around the world. The data included the date of the subway system opening, the location of the subway system, and the size of the subway system. manually collected data on the latitude, longitude, and date of opening of every subway station in the world between January 2012 and February 2014. They updated the data in 2020 using online sources and Google Maps. The data were used to construct a monthly panel that describes the count of operational stations in each subway city between February 2000 and December 2017, which was the time period for which air pollution data were available.

@@

## Possible Condounding Variables
To account for other factors that could affect particulate concentrations, such as changes in weather or seasonal variations, the study used a variety of statistical techniques, including regression analysis and fixed effects models. The study also controlled for other variables that could affect air pollution, such as population density, income levels, and proximity to industrial areas.

@@

>>>>

The paper investigates the impact of subway systems on air pollution in cities around the world. It uses two main data sources: a description of the world's subway systems and a measure of airborne particulates, Aerosol Optical Depth (AOD), recorded by satellites between February 2000 and December 2017. The analysis uses a comparison of changes in AOD within a city before and after the opening of a subway system to establish its causal effect. Most of the data and basic analysis are from Nicolas Gendron-Carrier's paper of "Subways and Urban Air Pollution". (\@ Subways and Urban Air Pollution)

@@

# Data

All the data that is used for replication in this paper is collected by Nicolas Gendron-Carrier et al. Their study collected data from multiple sources and employed various techniques to analyze the data and draw conclusions about the impact of subway systems on air pollution.

## Pollution Measured by Satellite

The study used satellite imagery to measure the concentration of particulates in the air. The study uses data from satellites to measure the aerosol optical depth (AOD) of the atmosphere at a 3km spatial resolution. The Moderate Resolution Imaging Spectroradiometers on Terra and Aqua earth-observing satellites provide daily AOD measures. The satellite data was collected from the NASA MODIS instrument, which provides measurements of particulate matter at a resolution of 10 kilometers. The satellite data was then combined with ground-based measurements of particulate matter to create a comprehensive dataset that could be used to analyze the impact of subway systems on air pollution. (@Remer, L. A., S. Mattooand R. C. Levy, and L. A. Munchak. 2013. Modis 3km aerosol product: algorithm and global perspective. Atmospheric Measurement Techniques 6: 1829--1844.)

## Subway Data

Furthermore, the study also collected data on the opening of subway systems in various cities around the world. The data included the date of the subway system opening, the location of the subway system, and the size of the subway system. manually collected data on the latitude, longitude, and date of opening of every subway station in the world between January 2012 and February 2014. They updated the data in 2020 using online sources and Google Maps. The data were used to construct a monthly panel that describes the count of operational stations in each subway city between February 2000 and December 2017, which was the time period for which air pollution data were available.

@@

## Possible Condounding Variables

To account for other factors that could affect particulate concentrations, such as changes in weather or seasonal variations, the study used a variety of statistical techniques, including regression analysis and fixed effects models. The study also controlled for other variables that could affect air pollution, such as population density, income levels, and proximity to industrial areas.

@@

## Part Three

```{r}
{r}
library(here)
library(dplyr)

subway_city <- read.csv(file = '/Users/lucas/Documents/paper2/subway_date_construction_begins_V2_AEJ_revision.csv')

subway_city
```

The scatterplot that this code generates displays the correlation between the start of work and the opening date for various cities. Using the ggplot tool from the ggplot2 library, a scatterplot is produced. The x and y aesthetic mappings are defined as the start of construction and the opening date, respectively, in the data frame subway city that houses the information. To depict each individual data point on the plot, points are added using the geom point function.

Additionally, two smoothed lines are added by the code to the plot in order to highlight the data's pattern and overall distributional shape. A linear regression line is the first flattened line, and a smoothed curve called a Loess curve is the second smoothed line.

```{r}
library(ggplot2)

ggplot(subway_city, aes(x = Begin.construction.date, y = Opening.date)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_smooth(method = "loess", se = FALSE, color = "red") +
  geom_text(aes(label = City), hjust = -0.2, vjust = 1.2, size = 1.5) +
  labs(x = "Begin construction date", y = "Opening date", title = "Opening date vs. Begin construction date for cities")

```{r}
new_subway_city <- subway_city |>
  select(-Links,-Notes) |>
  arrange(Opening.date)
```

```{r}
library(knitr)
kable(head(new_subway_city,10), caption = "Table 1: Subway_City (First 5 rows)")
```
